Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2023-05-24 src/naomi-simple_ks/ks.Rmd
Produce beta_anc_rho output too in KS

```{r}
pars_eval <- pars %in% c("beta_rho", "u_rho_x")
names(pars_eval) <- pars
```

@@

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("beta_alpha")
```

@@

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("beta_lambda")
```

@@

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf("beta_anc_rho")
```

@@

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf("beta_anc_alpha")
```

@@

```{r}
ks_helper("beta", starts_with = TRUE)

#' Save off KS results for one parameter as example
saveRDS(
  to_ks_df(par = "beta_alpha", starts_with = TRUE),
  file = "beta_alpha.rds"
)
```

>>>>

```{r}
pars_eval <- pars %in% c("beta_rho", "beta_alpha", "beta_anc_rho", "u_rho_x")
names(pars_eval) <- pars
```

@@

```{r eval = pars_eval[["beta_alpha"]]}
beta_alpha <- histogram_and_ecdf("beta_alpha", return_df = TRUE)
beta_alpha$plot

#' Save off KS results as example
saveRDS(
  beta_alpha$df_compare,
  file = "beta_alpha.rds"
)
```

@@

```{r eval = pars_eval[["beta_lambda"]]}
histogram_and_ecdf_helper("beta_lambda")
```

@@

```{r eval = pars_eval[["beta_anc_rho"]]}
beta_anc_rho <- histogram_and_ecdf("beta_anc_rho", i = 1, return_df = TRUE)
beta_anc_rho$plot

#' Save off KS results as example
saveRDS(
  beta_anc_rho$df_compare,
  file = "beta_anc_rho.rds"
)
```

@@

```{r eval = pars_eval[["beta_anc_alpha"]]}
histogram_and_ecdf("beta_anc_alpha")
```

@@

```{r}
ks_helper("beta", starts_with = TRUE)
```
